\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-17 paper.tex
fix float issues after removing too much
a bit of rephrasing

@@

These taxonomies focus on the act of detecting intrusions itself, the local
algorithm so to speak. In a highly distributed environment, the orthogonal
categorization, dealing with the distributed algorithm, is maybe even more
important: how do algorithms deal with the information coming from the group
they are part of?

@@

A research topic that exists in parallel to the detection and cooperation
duality is software attestation. Software attestation offers algorithms for
exchanging information about the software that is running on a node, and aims
to identify nodes that can no longer prove that their content is unaltered.
Examples of a family of algorithms to implement this functionality include
SWATT\cite{seshadri2004swatt}, ICE/SCUBA\cite{seshadri2006scuba} and
SAKE\cite{seshadri2008sake}.

>>>>

\usepackage{float}

@@

These taxonomies focus on the act of detecting intrusions themselves. In a
highly distributed environment, an orthogonal categorization, dealing with the
distributed nature of the network, may be even more important.

@@

A research topic that exists in parallel to the detection and cooperation
duality is software attestation. It offers algorithms for exchanging
information about the software that is running on a device, and aims to
identify devices that can no longer prove that their content is unaltered. A
family of algorithms to implement this functionality are
SWATT\cite{seshadri2004swatt}, ICE/SCUBA\cite{seshadri2006scuba} and
SAKE\cite{seshadri2008sake}.
